Context Inconsistency Management \\in Pervasive Systems

### 2011-03-21 paper/paper.tex
extend introduction
some tweaks - pdfify
add section

In pervasive computing, contexts are used to make applications perform a certain action. Contexts can be seen as pieces of environmental information, which the applications depend on. Sometimes contexts are not consistent due to crossreads and misreads. The correctness of the contexts can be checked by evaluating the consistency constraints associated to them. There are multiple ways to check for consistency constraints. Constaint checking techniques are split up in two classes: Non-incremental checking and incremental checking. Incremental checking consists also of two classes: Entire Constraint Checking and Partial Constraint Checking. Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts. The algoritms use specific datastructures, like ontology models, in order to resolve the inconsistencies. However, certain conflict resolving algorithms are too slow for use in practice. This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice.

@@

@@

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{paper}

\appendix
\section{Fuzzy Ontology Calculations}
Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
\begin{align}
                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
                                    &= .01152 * c_1\\
                                    &= 0.9998\\
                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
                                    &= 0.000002813 * c_1\\
                                    &= 0.0002\\
\end{align}
Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
\begin{align}
                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
                                    &= 0.000045 * c_2\\
                                    &= 0.059\\
                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
                                    &= 0.00072 * c_2\\
                                    &= 0.941\\
\end{align}
\end{document}

>>>>

In pervasive computing, contexts are used to make applications perform a certain action. Contexts can be seen as pieces of environmental information, which the applications depend on. Sometimes contexts are not consistent due to crossreads and misreads. The correctness of the contexts can be checked by evaluating the consistency constraints associated to them. There are multiple ways to check for consistency constraints. Constaint checking techniques are split up in two classes: Non-incremental checking and incremental checking. Incremental checking consists also of two classes: Entire Constraint Checking and Partial Constraint Checking. Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts. The algoritms use specific datastructures, like ontology models, in order to resolve the inconsistencies. However, certain conflict resolving algorithms are too slow for use in practice. This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice. Another approach to handling context inconsistencies is representing them into the context model, as opposed to resolving them. This can be done efficiently by using fuzzy ontologies in a tree like structure, as we show in a use case.

@@

\section{From Ontology to CCT}
As stated above the Partial Constraint Checking (PCC) algorithm is much faster than Entire Constraint Checking due to the fact that a Consistency Computation Tree (CCT) is used to store the constraints belonging to a (set of) context(s). We also stated that the ontology based context model is the most promising type of model to capture context information. Although the context model appears as a tree (see Fig. \ref{fig:ont}), the PCC algorithm cannot be directly applied to it.

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{Ontology.eps}
  \caption{An example of an ontology based context model Source:~\cite{bu:2006:CCM}}
  \label{fig:ont}
\end{figure}

The model is actually a part of a larger ontology, but it is sufficient for this section. Now it needs to be transformed into a CCT for PCC. With a CCT the main focus should be on the context set of a single entity in the model. The transformation itself can be done automatically with a depth-first search algorithm, but there is no such algorithm available at this time. However, we can give a few examples of the CCT based on this ontology model. The context set of the entity \textit{Student} will be focused on. Lets say that the entity \textit{Student} is located in the \textit{Place} entity \textit{Road}, then the CCT will look as the upper tree in Fig. \ref{fig:cct1}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{smallCCT1.eps}
  \caption{The CCTs of \textit{Student}}
  \label{fig:cct1}
\end{figure}

If the system suddenly decides that \textit{Student} is located in a \textit{Lab}, then the tree will be updated to the lower tree. Note that the system can decide in a multitude of ways that \textit{Student} is located in the \textit{Lab} by for example invalidating the earlier constraint branch after a certain amount of time or by for example basing the new \textit{Place} on the information in a new context set. Also note that the leaf of a branch cannot contain an entity that is not available in the context model. So \textit{Student} cannot be located in, for example, \textit{Car}, because it is not part of the model. Even if the location in a context would be \textit{Car}, then the system would consider the location as an inconsistency in the context and detect it very quickly with PCC.

@@

Then we have shown examples of CCTs of entitities in an ontology based context model. We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time. However, with the definitions of OWL one can create a depth-first search algorithm that transforms an ontology in multiple CCTs (one for each leaf entity in the model).

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{paper}
\newpage
\appendix
\section{Fuzzy Ontology Calculations}
Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
\begin{align}
                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
                                    &= .01152 * c_1\\
                                    &= 0.9998\\
                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
                                    &= 0.000002813 * c_1\\
                                    &= 0.0002
\end{align}
Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
\begin{align}
                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
                                    &= 0.000045 * c_2\\
                                    &= 0.059\\
                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
                                    &= 0.00072 * c_2\\
                                    &= 0.941
\end{align}
\end{document}
